The single asset test cases are designed to test the basic elements of the event-based risk calculator, such as:

\begin{itemize}
\item asset event loss table computation
\item asset loss exceedance curve computation
\end{itemize}

The location and taxonomy of the single asset in the exposure model used for the single-asset test cases for the event-based risk calculator are given in Table \ref{tab:asset}.

% ---------------------------------------------------------------------------
\subsubsection{Case 1a}
\input{qareport/cases/ebr-1a}
\input{qareport/results/ebr-1a}
Table \ref{tab:result-ebr-1a} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1b}
\input{qareport/cases/ebr-1b}
\input{qareport/results/ebr-1b}
Table \ref{tab:result-ebr-1b} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1c}
\input{qareport/cases/ebr-1c}
\input{qareport/results/ebr-1c}
Table \ref{tab:result-ebr-1c} shows the comparison of the OpenQuake result for average annual loss with the expected result.
% ---------------------------------------------------------------------------
\subsubsection{Case 1d}
\input{qareport/cases/ebr-1d}
\input{qareport/results/ebr-1d}
Table \ref{tab:result-ebr-1d} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1e}
\input{qareport/cases/ebr-1e}
\input{qareport/results/ebr-1e}
Table \ref{tab:result-ebr-1e} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1f}
\input{qareport/cases/ebr-1f}
\input{qareport/results/ebr-1f}
Table \ref{tab:result-ebr-1f} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1g}
\input{qareport/cases/ebr-1g}
\input{qareport/results/ebr-1g}
Table \ref{tab:result-ebr-1g} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2a}
\input{qareport/cases/ebr-2a}
\input{qareport/results/ebr-2a}
Table \ref{tab:result-ebr-2a} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2b}
\input{qareport/cases/ebr-2b}
\input{qareport/results/ebr-2b}
Table \ref{tab:result-ebr-2b} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2c}
\input{qareport/cases/ebr-2c}
\input{qareport/results/ebr-2c}
Table \ref{tab:result-ebr-2c} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2d}
\input{qareport/cases/ebr-2d}
\input{qareport/results/ebr-2d}
Table \ref{tab:result-ebr-2d} shows the comparison of the OpenQuake result for average annual loss with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 3a}
\input{qareport/cases/ebr-3a}
\input{qareport/results/ebr-3a}
Table \ref{tab:result-ebr-3a} shows the comparison of the OpenQuake result for average annual loss with the expected result.
