The single asset test cases are designed to test the basic elements of the classical-PSHA based damage calculator, such as:

\begin{itemize}
\item damage state occurrence probabilities for assets
\end{itemize}

The location and taxonomy of the single asset in the exposure model used for the single-asset test cases for the classical damage calculator are given in Table \ref{tab:assets}.


% ---------------------------------------------------------------------------
\subsubsection{Case 1a}
Test case 1a 

\input{qareport/results/cd-1a}

Table \ref{tab:result-cd-1a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1b}
Test case 1b 

\input{qareport/results/cd-1b}

Table \ref{tab:result-cd-1b} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1c}


\input{qareport/results/cd-1c}

Table \ref{tab:result-cd-1c} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2a}


\input{qareport/results/cd-2a}

Table \ref{tab:result-cd-2a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2b}


\input{qareport/results/cd-2b}

Table \ref{tab:result-cd-2b} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 3a}


\input{qareport/results/cd-3a}

Table \ref{tab:result-cd-3a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 4a}


\input{qareport/results/cd-4a}

Table \ref{tab:result-cd-4a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 4b}


\input{qareport/results/cd-4b}

Table \ref{tab:result-cd-4b} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 4c}


\input{qareport/results/cd-4c}

Table \ref{tab:result-cd-4c} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 5a}


\input{qareport/results/cd-5a}

Table \ref{tab:result-cd-5a} shows the comparison of the OpenQuake result with the expected result.
