The single asset test cases are designed to test the basic elements of the scenario risk calculator, such as:

\begin{itemize}
\item basic loss field computation
\item calculation of mean and standard deviation of scenario loss
\end{itemize}

\input{qareport/tables/tab-asset.tex}

The location and taxonomy of the single asset in the exposure model used for the single-asset test cases for the scenario risk calculator are given in Table \ref{tab:asset}.

% ---------------------------------------------------------------------------
\subsubsection{Case 1a}
\input{qareport/cases/sr-1a}
\input{qareport/results/sr-1a}
Table \ref{tab:result-sr-1a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1b}
\input{qareport/cases/sr-1b}
\input{qareport/results/sr-1b}
Table \ref{tab:result-sr-1b} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1c}
\input{qareport/cases/sr-1c}
\input{qareport/results/sr-1c}
Table \ref{tab:result-sr-1c} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1d}
\input{qareport/cases/sr-1d}
\input{qareport/results/sr-1d}
Table \ref{tab:result-sr-1d} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1e}
\input{qareport/cases/sr-1e}
\input{qareport/results/sr-1e}
Table \ref{tab:result-sr-1e} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1f}
\input{qareport/cases/sr-1f}
\input{qareport/results/sr-1f}
Table \ref{tab:result-sr-1f} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1g}
\input{qareport/cases/sr-1g}
\input{qareport/results/sr-1g}
Table \ref{tab:result-sr-1g} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1h}
\input{qareport/cases/sr-1h}
\input{qareport/results/sr-1h}
Table \ref{tab:result-sr-1h} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2a}
\input{qareport/cases/sr-2a}
Table \ref{tab:result-sr-2a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2b}
\input{qareport/cases/sr-2b}
Table \ref{tab:result-sr-2b} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2c}
\input{qareport/cases/sr-2c}
Table \ref{tab:result-sr-2c} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2d}
\input{qareport/cases/sr-2d}
\input{qareport/results/sr-2a}
\input{qareport/results/sr-2b}
\input{qareport/results/sr-2c}
\input{qareport/results/sr-2d}
Table \ref{tab:result-sr-2d} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 3a}
\input{qareport/cases/sr-3a}
\input{qareport/results/sr-3a}
Table \ref{tab:result-sr-3a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 3b}
\input{qareport/cases/sr-3b}
\input{qareport/results/sr-3b}
Table \ref{tab:result-sr-3b} shows the comparison of the OpenQuake result with the expected result.
% ---------------------------------------------------------------------------
\subsubsection{Case 3c}
\input{qareport/cases/sr-3c}
\input{qareport/results/sr-3c}
Table \ref{tab:result-sr-3c} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 3d}
\input{qareport/cases/sr-3d}
\input{qareport/results/sr-3d}
Table \ref{tab:result-sr-3d} shows the comparison of the OpenQuake result with the expected result.
