The single asset test cases are designed to test the basic elements of the classical-PSHA based risk calculator, such as:

\begin{itemize}
\item asset loss ratio exceedance curve computation
\item asset loss exceedance curve computation
\end{itemize}

The location and taxonomy of the single asset in the exposure model used for the single-asset test cases for the classical risk calculator are given in Table \ref{tab:assets}.

% ---------------------------------------------------------------------------
\subsubsection{Case 1a}
\input{qareport/cases/cr-1a}
\input{qareport/results/tab-result-cr-1a}
Table \ref{tab:result-cr-1a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1b}
Test case 1b 

\input{qareport/results/tab-result-classical-risk-1b}

Table \ref{tab:result-classical-risk-1b} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1c}


\input{qareport/results/tab-result-classical-risk-1c}

Table \ref{tab:result-classical-risk-1c} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1d}


\input{qareport/results/tab-result-classical-risk-1d}

Table \ref{tab:result-classical-risk-1d} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 1e}


\input{qareport/results/tab-result-classical-risk-1e}

Table \ref{tab:result-classical-risk-1e} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2a}


\input{qareport/results/tab-result-classical-risk-2a}

Table \ref{tab:result-classical-risk-2a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2b}


\input{qareport/results/tab-result-classical-risk-2b}

Table \ref{tab:result-classical-risk-2b} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2c}


\input{qareport/results/tab-result-classical-risk-2c}

Table \ref{tab:result-classical-risk-2c} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 2d}


\input{qareport/results/tab-result-classical-risk-2d}

Table \ref{tab:result-classical-risk-2d} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 3a}


\input{qareport/results/tab-result-classical-risk-3a}

Table \ref{tab:result-classical-risk-3a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 4a}


\input{qareport/results/tab-result-classical-risk-4a}

Table \ref{tab:result-classical-risk-4a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 4b}


\input{qareport/results/tab-result-classical-risk-4b}

Table \ref{tab:result-classical-risk-4b} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 4c}


\input{qareport/results/tab-result-classical-risk-4c}

Table \ref{tab:result-classical-risk-4c} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 5a}


\input{qareport/results/tab-result-classical-risk-5a}

Table \ref{tab:result-classical-risk-5a} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 5b}


\input{qareport/results/tab-result-classical-risk-5b}

Table \ref{tab:result-classical-risk-5b} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 5c}


\input{qareport/results/tab-result-classical-risk-5c}

Table \ref{tab:result-classical-risk-5c} shows the comparison of the OpenQuake result with the expected result.

% ---------------------------------------------------------------------------
\subsubsection{Case 5d}


\input{qareport/results/tab-result-classical-risk-5d}

Table \ref{tab:result-classical-risk-5d} shows the comparison of the OpenQuake result with the expected result.