The purpose of this case is to test the basic elements of a scenario risk calculation involving multiple assets, such as the computation of the mean and standard deviation of the total loss for a portfolio of assets.

\input{qareport/tables/tab-assets-tax3}
The list of assets and their taxonomies are shown in Table~\ref{tab:assets-tax3}.

Five precomputed ground motion fields are used as the starting point for this case. These ground motion fields take into consideration both the inter-event and intra-event variability in the ground motion. The ground motion prediction equation used is \citet{boore2008}, and the \citet{jayaram2009} model for spatial correlation of ground motion values is applied.

\input{qareport/tables/tab-gmfs-diff-l7-5}

Table~\ref{tab:gmfs-diff-l7-5} lists the ground motion fields used in this test case.


\input{qareport/tables/tab-vf-ln-tax3-zcov}

Table~\ref{tab:vf-ln-tax3-zcov} shows the mean loss ratios and corresponding coefficients of variation in the vulnerability function used in this test case.

Since there is no variability in the loss ratio, calculation of the loss ratios is straightforward in this case. Consider asset $a3$, which has the taxonomy $tax1$.  The ground motion values at the location of the single asset are $[0.15, 0.05, 0.05, 0.15, 0.15] g$. Consider the first value of $PGA = 0.15 g$. The vulnerability function for this taxonomy provides mean loss ratio values at intensity measure levels $0.05 g$ and $0.20 g$, but none at $0.15 g$. The mean loss ratios at $0.05 g$ and $0.20 g$ are $0.01$ and $0.04$ respectively.

The mean loss ratio at $0.15 g$ is obtained by interpolating between these two values. Linear interpolation gives a mean loss ratio of $0.03$ for $PGA = 0.15 g$.

Similar interpolation for the other ground motion values gives mean loss ratios of $0.01$, $0.01$, $0.03$, and $0.03$ respectively. These numbers are multiplied by the asset value for $a1$ of $10,000$ to give loss values for asset $a1$ of $[300, 100, 100, 300, 300]$.

Repeating this exercise for the six other assets, using the appropriate vulnerability function for each taxonomy, we get the following loss values for the five ground motion fields:

\begin{itemize}
	\item $a1$: $[550, 4490, 1300, 3385, 9300]$
	\item $a2$: $[180, 215, 186.67, 680, 740]$
	\item $a3$: $[1800, 2585, 1900, 3235, 9300]$
	\item $a4$: $[1620, 2250, 1710, 2750, 8200]$
	\item $a5$: $[430, 360, 120, 2780, 4575]$
	\item $a6$: $[470, 1520, 260, 335, 1205]$
	\item $a7$: $[280, 1150, 460, 1550, 550]$
\end{itemize}

The portfolio losses are obtained simply as the sum of all the individual asset losses for each ground motion field. The portfolio losses are: $[5330, 12570, 5936.67, 14715, 33870]$.

Now, the mean and standard deviation of the scenario loss can be calculated for each of the individual assets, as well as for the portfolio.